\documentclass{beamer}


\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{ragged2e}  % `\justifying` text
\usepackage{booktabs}  % Tables
\usepackage{tabularx}
\usepackage{tikz}      % Diagrams
\usetikzlibrary{calc, shapes, backgrounds}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage{url}       % `\url
\usepackage{listings}  % Code listings
\usepackage[T1]{fontenc}
\usepackage{caption}
\usepackage{hyperref}

\usepackage{beamerthemehbrs}


\begin{document}

%\begin{frame}
%    \titlepage
%\end{frame}

\begin{frame}
        \frametitle{General Code Skeleton}
            \begin{itemize}
                \item The code is divided into two classes namely
                \begin{enumerate}
                    \item Repository
                    \item Safety monitors
                \end{enumerate}
                \item \textbf{Repository} is the central component in the architecture. It contains knowledge for deployment.
                \item The safety monitors are detected and transfers information to other components for deployment.
                \item It also notifies about the changes in repository to all other components in the system.
                \item \textbf{Safety Monitor} class perform selection of the safety monitor followed by finding the suitable platform and deploying them.
            \end{itemize}
    \end{frame}
    
\begin{frame}{}
    \begin{itemize}
        \item It contains get-acceptable-platform() which returns platform that satisfy the given requirements by means of Constraint Satisfaction Problem (CSP).
        \item CSP is implemented using MiniZinc(mzn) library - python based. 
        \item The requirements are formulated into suitable constraints and platforms that satisfy the given constraints will be selected.
        \item Finally the safety monitor will be deployed in the selected platform using deploy().
        %\item Code: \url{https://github.com/AshAswin/Adaptive-Deployment-of-Safety-Monitors-of-Autonomous-Systems/blob/Jithsaavvy-code-skeleton/code_skeleton.py}
        \item \href{https://github.com/AshAswin/Adaptive-Deployment-of-Safety-Monitors-of-Autonomous-Systems/blob/Jithsaavvy-code-skeleton/code_skeleton.py}{\textbf{Code - GitHub}}
        
    \end{itemize}
    
\end{frame}
    

\end{document}
